Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-03 report.Rmd
clean names

```{r}
targets::tar_load("fit_sp_0_summary_simple")
targets::tar_load("fit_sp_1_summary_model")
targets::tar_load("fit_sp_11_summary_model")
targets::tar_load("fit_sp_2_summary_model")
targets::tar_load("fit_sp_3_summary_model")
targets::tar_load("fit_sp_4_summary_sma")
targets::tar_load("fit_sp_5_summary_sma")
targets::tar_load("fit_sp_6_summary_sma_err")

targets::tar_load("fit_sp_0_diagnostics_simple")
targets::tar_load("fit_sp_1_diagnostics_model")
targets::tar_load("fit_sp_11_diagnostics_model")
targets::tar_load("fit_sp_2_diagnostics_model")
targets::tar_load("fit_sp_3_diagnostics_model")
targets::tar_load("fit_sp_4_diagnostics_sma")
targets::tar_load("fit_sp_5_diagnostics_sma")
targets::tar_load("fit_sp_6_diagnostics_sma_err")
```

```{r}
fit_sp_0_summary_simple |> filter(rhat > 1.1)
fit_sp_1_summary_model |> filter(rhat > 1.1)
fit_sp_11_summary_model |> filter(rhat > 1.1)
fit_sp_2_summary_model |> filter(rhat > 1.1)
fit_sp_3_summary_model |> filter(rhat > 1.1)
fit_sp_4_summary_sma |> filter(rhat > 1.1)
fit_sp_5_summary_sma |> filter(rhat > 1.1)
fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
```

@@

```{r}
div_check(fit_sp_0_diagnostics_simple)
div_check(fit_sp_1_diagnostics_model)
div_check(fit_sp_11_diagnostics_model)
div_check(fit_sp_2_diagnostics_model)
div_check(fit_sp_3_diagnostics_model)
div_check(fit_sp_4_diagnostics_sma)
div_check(fit_sp_5_diagnostics_sma)
div_check(fit_sp_6_diagnostics_sma_err)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]], loo_model[[5]])
```

@@

>>>>

```{r,eval=TRUE}

targets::tar_load(fit_sp_no_lma_summary_model)
targets::tar_load(fit_sp_no_lma_int_summary_model)
targets::tar_load(fit_sp_lma_summary_model)
targets::tar_load(fit_sp_lma2_summary_model2)
targets::tar_load(fit_sp_ld_summary_model)
targets::tar_load(fit_sp_ld2_summary_model)
targets::tar_load(fit_sp_ld3_summary_model)
targets::tar_load(fit_sp_lm_summary_model)
targets::tar_load(fit_sp_lma0_summary_simple)

targets::tar_load(fit_sp_no_lma_diagnostics_model)
targets::tar_load(fit_sp_no_lma_int_diagnostics_model)
targets::tar_load(fit_sp_lma_diagnostics_model)
targets::tar_load(fit_sp_lma2_diagnostics_model2)
targets::tar_load(fit_sp_ld_diagnostics_model)
targets::tar_load(fit_sp_ld2_diagnostics_model)
targets::tar_load(fit_sp_ld3_diagnostics_model)
targets::tar_load(fit_sp_lm_diagnostics_model)
targets::tar_load(fit_sp_lma0_diagnostics_simple)

```

```{r,eval=TRUE}
fit_sp_no_lma_summary_model  |> filter(rhat > 1.1)
fit_sp_no_lma_int_summary_model |> filter(rhat > 1.1)
fit_sp_lma_summary_model |> filter(rhat > 1.1)
fit_sp_lma2_summary_model2 |> filter(rhat > 1.1)
fit_sp_ld_summary_model |> filter(rhat > 1.1)
fit_sp_ld2_summary_model |> filter(rhat > 1.1)
fit_sp_ld3_summary_model |> filter(rhat > 1.1)
fit_sp_lm_summary_model |> filter(rhat > 1.1)
fit_sp_lma0_summary_simple |> filter(rhat > 1.1)
```

@@

```{r,eval=TRUE}
div_check(fit_sp_no_lma_diagnostics_model)
div_check(fit_sp_no_lma_int_diagnostics_model)
div_check(fit_sp_lma_diagnostics_model)
div_check(fit_sp_lma2_diagnostics_model2)
div_check(fit_sp_ld_diagnostics_model)
div_check(fit_sp_ld2_diagnostics_model)
div_check(fit_sp_ld3_diagnostics_model)
div_check(fit_sp_lm_diagnostics_model)
div_check(fit_sp_lma0_diagnostics_simple)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(
  loo_model[[1]], loo_model[[2]], loo_model[[3]],
  loo_model[[4]], loo_model[[5]], loo_model[[6]],
  loo_model[[7]], loo_model[[8]], loo_model[[9]])
```

@@

## species simple

```{r, eval=TRUE}
tar_load(sma_sp_2_tab)
sma_sp_2_tab |>
  kable() |>
  kable_styling()
```
